Declarative Integration of Interactive 3D Graphics into the World-Wide Web:\\Principles, Current Approaches, and Research Agenda

### 2013-04-25 Web3D2013-Dec3D/paper.tex
Switched position of Polyfill and Essential subsections and added some text to better link the subsections

As already mentioned, the Dec3D Community Group \cite{Dec3D} has been formed to determine the requirements, options, and use cases for the declarative integration of interactive 3D graphics capabilities into the Web technology stack, which will provide a foundation for future standardization. While this standardization is our goal, we still need platforms allowing for the experimentation and for the assessment of our design decisions. We also need to reach out to Web developers who could provide us with valuable feedback as early as possible.

@@

\subsection{X3DOM and XML3D}

With X3DOM \cite{Behr2009} and XML3D \cite{Sons2010} two open-source frameworks are available, which are briefly introduced in this section. Both frameworks support the ongoing discussion in the computer graphics and Web communities how an integration of HTML(5) and Declarative 3D content could look like. This discussion is followed by the presentation of the so-called ``polyfill'' approach for further development activities.

@@

% TODO: In the last paragraph of this section, we can write about the efforts to consolidate approaches and/or how the competing two frameworks influence one another for the common benefit...? This should be followed by the some link to the next section (polyfill).

\subsection{Polyfill Approach}

@@

\subsection{Declarative 3D Essentials}

In this section we briefly outline our proposed essential elements for an upcoming Dec3D standard. First of all, a start element allows the transition from the HTML flow layout to 3D transformations:

>>>>

As already mentioned, the Dec3D Community Group \cite{Dec3D} has been formed to determine the requirements, options, and use cases for the declarative integration of interactive 3D graphics capabilities into the Web technology stack, which will provide a foundation for future standardization. While this standardization is our goal, we still need platforms allowing for the experimentation and evaluation of our design decisions~(\ref{subsection:evaluation}). We also need to reach out to Web developers who could provide us with valuable feedback as early as possible. From the evaluations we extract the essential features~(\ref{subsection:essentials}) for a declarative approach. Finally, we check the level of integration we can achieve, emulating these features using existing technologies~(\ref{subsection:polyfill}).

@@

\subsection{Evaluation platforms}
\label{subsection:evaluation}
With X3DOM \cite{Behr2009} and XML3D \cite{Sons2010} two evaluation platforms are available to support the ongoing discussion in the computer graphics and Web communities how an integration of HTML(5) and Declarative 3D content could look like.

@@

Both platforms are available under an Open Source license and used in many national and international research projects. From the user feedback and use-cases we were able to collect from the evaluation platforms, we were able to derive the essential features, that both approaches have in common and that we propose for a Dec3D standard.

% TODO: In the last paragraph of this section, we can write about the efforts to consolidate approaches and/or how the competing two frameworks influence one another for the common benefit...? This should be followed by the some link to the next section (polyfill).
\subsection{Declarative 3D Essentials}
\label{subsection:essentials}
In this section we briefly outline our proposed essential elements for an upcoming Dec3D standard. First of all, a start element allows the transition from the HTML flow layout to 3D transformations:

\subsection{Polyfill Approach}
\label{subsection:polyfill}

@@
